### 2019-08-09 Thesis/pages/design.tex
Changes; - Added data from final round of experiments - Updated all batch files - Added more discussion to the expeirment section of the report
Changes; - Updated and read through aspects of the report - Continuing with implementation aspects of the project

This chapter will discuss and overview of the proposed attack and the elements that are required.

@@

Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations. There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
The limited combinations will result in matches of a limited quality. This will require consideration later in the project.

@@

It also allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex. It was in use right up the end of 1998 within various US Government departments. Due to this prolific stature and proven track record it was deemed suitable as one of the selected similarity metrics.

\subsection{Metaphone}
Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex. It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation. Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.

Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips. The original version was chosen due to its historical and widespread usage.

\subsection{Levenshtien Distance}
Levenshtein distance is a string metric designed to measure the 'distance' between two strings. It is simply the number of single-character edits (insertions, deletions or substitutions) required to reach the other string. Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} Levenshtien distance was deemed another suitable metric.

@@

Extensive prior work has gone into producing models of features that map to phonemes. \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}. Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language. The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.

@@

For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with multiplication allowing the 'tinting' words with a theme.

The ability to perform operations and measure dissimilarity allows for a plethora of applications. One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximized. This, if the vector mappings are an accurate representation could allow a creation of a phonetically distinctive wordlist. This will be discussed further at a later stage of the report.

@@

The first was the addition of five "Random matches" questions. These were two random words selected from the dictionary. Therefore, the overall rating of these words should be close to an average of 1. This allows a simple check to see if the user is providing valid results. If their average is too high, the results will be discarded.

@@

\subsubsection{Considerations}

\textbf{TODO: } Talk more about how the proposed idea of audio-audio would be very expensive etc etc. I need to remove the bit in the Experiment chapter and place it here.

\label{sec:exp1_considerations}
This section will discuss the considerations required when interpreting the results of the study.

The first consideration is the way the words are compared. Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual. This is because a user needs to match a words sound to the one displayed on their device. In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them. Therefore, this experiment does not fully capture the targeted scenario. This was decided partly to aforementioned lack of resources. The main design of the experiment was to provide a simple way to cull the large number of metrics. The initial choice of five metrics discussed in Section \ref{sec:metrics} was to be followed by a more empirical decision. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics.

@@

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. However, we believe that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end. All these aspects, however, will require empirical evidence to arrive at a conclusion. Therefore, this consideration will need to be made when assessing the results of the experiment.

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days on with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments).

@@

Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations makes the attack search quicker as there are more possibilities.

Any key that exceeds this criteria is deemed as vulnerable is one of the three attack contexts. A list of these vulnerable keys are sampled from when an attack is simulated. The percentage of vulnerable keys will be explored in Chapter \ref{cha:Experiments}.

\subsubsection{Quality control}
As the previous experiment, participants will be sourced from MTurk. Therefore, again, quality control is and aspect that requires consideration. As with the previous study, initially screened native speakers will be used. The same process will be performed to recruit suitable workers. Two metrics will be used to detect invalid results. Audio button clicks and overall time taken.

@@

\subsubsection{Considerations}
\textbf{TODO}

Demographics of MTurk workers (Discussed in the previous section)

>>>>

This chapter will discuss and overview of the proposed designs for elements required to answer the research questions. Alternative designs are explained when relevant and design choices are justified

@@

Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations. There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
The limited combinations will result in matches of a limited quality.

@@

It also allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex. It was in use right up the end of 1998 within various US Government departments. Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.

\subsection{Metaphone}
Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex. It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation. Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}. Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.

\textbf{TODO} Better argument needed?

Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.

\subsection{Levenshtein Distance}
Levenshtein distance is a string metric designed to measure the 'distance' between two strings. It is simply the number of single-character edits (insertions, deletions or substitutions) required to reach the other string. Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} Levenshtien distance was deemed another suitable metric. Levenshtein is also the most algorithmically simplistic of all the options, this further contributes to its appeal as a chosen metric.

@@

Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}. Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language. The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.

@@

For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with examples like multiplication allowing the `tinting' words with a theme.

The ability to perform operations and measure dissimilarity allows for a plethora of applications. One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximized. This, if the vector mappings are an accurate representation could allow a creation of a phonetically distinctive wordlist. These unique aspects contributes to inclusion of this metric in the set.

@@

The first was the addition of five "Random matches" questions. These are matches consisting of two random words selected from the dictionary. Therefore, the expected average rating of these words should be close to 1. This allows a simple check to see if the user is providing valid results. If their average is too high, the results will be discarded.

@@

\subsubsection{Considerations}
\label{sec:exp1_considerations}

The first consideration is the way the words are compared. Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual. This is because a user needs to match a words sound to the one displayed on their device. In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them. This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. This has the potential to affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words. The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. This, however, adds a substantial cost onto the operation of the study. Due to the aforementioned lack of resources the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

@@

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. We believe, however, that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end. All these aspects will require empirical evidence to arrive at a conclusion. Therefore, this consideration will need to be made when assessing the results of the experiment.

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days on with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments). Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement. This is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations makes the attack search quicker as there are more possibilities. Any key that exceeds this criteria is deemed as vulnerable is one of the three attack contexts. A list of these vulnerable keys are sampled from when an attack is simulated. The percentage of vulnerable keys will be explored in Chapter \ref{cha:Experiments}.

\todo{Talk here about the sampling of vuln keys from keys harvested from PGP key servers.}

\subsubsection{Quality control}
\label{sec:exp2_quality}
As the previous experiment, participants will be sourced from MTurk. Therefore, again, quality control is and aspect that requires consideration. As with the previous study, initially screened native speakers will be used. The same process will be performed to recruit suitable workers. Two metrics will be used to detect invalid results. Audio button clicks and overall time taken.

@@

\subsubsection{Considerations}
As with the previous experiment MTurk demographics will result in participants that are not reflective of the general population. Due to the attack context of this experiment is can be assumed that the youth of the participants will contribute to less successful attacks. Therefore, the results generated by this experiment can be loosely assumed as a best case scenario for the scheme. We predict a high attack success rate if assessed over the general population.

### 2019-08-09 Thesis/pages/experiments.tex
Changes; - Updated and read through aspects of the report - Continuing with implementation aspects of the project

@@

The visual comparison will be the first point of contact between the question and the participant, then followed by the mental comparison of the phonetics. Therefore, this initial visual contact has the potential to bias the results of the study. This would affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words.
The alternative is to run the study with only audio based comparisons between words, this will force the user to compare just the phonetics of the words and not be influenced by the visuals of the pair. This, however, adds cost onto the time and execution of the study. Therefore, even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project due to a lack of project resources. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. Further work could aim to reproduce this study with the proposed audio based design.

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This makes this set of participants more educated that the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
% \begin{table}[!h]
%     \centering
%     \begin{tabular}{|l|l|}
%         \hline
%         Browser & Percentage \\
%         \hline
%         Chrome & 85.09\% \\
%         Firefox & 12.20\% \\
%         Safari & 1.90\% \\
%         Other & 0.81\% \\
%         \hline
%     \end{tabular}
%     \caption{Internet Browser breakdown}
%     \label{tab:exp2_browser}
%     \begin{tabular}{|l|l|}
%         \hline
%         Operating System & Percentage \\
%         \hline

%         \hline
%         Windows (All) & 74.26\% \\
%         ~~~~\textit{Windows 7} & ~~~12.74\% \\
%         ~~~~\textit{Windows 8} & ~~~4.07\% \\
%         ~~~~\textit{Windows 10} & ~~~57.45\% \\
%         MacOS X	 & 13.82\% \\
%         ChromeOS & 3.79\% \\
%         Android	& 4.34\% \\
%         iPhone	& 1.08\% \\
%         iPad	& 0.54\% \\
%         Linux	& 2.17\% \\
%         \hline
%     \end{tabular}
%     \caption{Operating System breakdown}
%     \label{tab:exp2_os}
% \end{table}

@@

\subsection{Comparison to alternative literature}
% # Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols

@@

\section{Distribution of keys permutations (Vuln-keys)}

>>>>

\section{Distribution of vulnerable keys}
\textbf{TODO}

\section{Average number of permutations for each metric}
\textbf{TODO}

@@

\textbf{TODO: } Reference back to the decisions made in the design section.

Therefore, even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project due to a lack of project resources.

This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. Further work could aim to reproduce this study with the proposed audio based design.

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This makes this set of participants more educated that the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.09\% \\
        Firefox & 12.20\% \\
        Safari & 1.90\% \\
        Other & 0.81\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

        \hline
        Windows (All) & 74.26\% \\
        ~~~~\textit{Windows 7} & ~~~12.74\% \\
        ~~~~\textit{Windows 8} & ~~~4.07\% \\
        ~~~~\textit{Windows 10} & ~~~57.45\% \\
        MacOS X	 & 13.82\% \\
        ChromeOS & 3.79\% \\
        Android	& 4.34\% \\
        iPhone	& 1.08\% \\
        iPad	& 0.54\% \\
        Linux	& 2.17\% \\
        \hline
    \end{tabular}
    \caption{Operating System breakdown}
    \label{tab:exp2_os}
\end{table}

@@

\subsection{Comparison to alternative literature}
\todo{Compare to the other similar papers, is this higher or lower than other papers?}

% # Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols

@@

### 2019-08-09 Thesis/pages/implementation.tex
Changes; - Updated and read through aspects of the report - Continuing with implementation aspects of the project

\textbf{TODO: } Talk here about the interesting and challenges that were overcome

@@

\section{First Experiment}
Explain how Google App Script was used?

\section{MainExperiment}
Design of the application etc

>>>>

\todo{Talk here about the interesting and challenges that were overcome}

@@

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used as the application. It provided functionality to easily present questions and record their responses. However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality other solution was required. This was solved by Google's  App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form. This allowed the re-sampling of matches each time a user submitted a response.

\begin{figure}[!h]
\begin{lstlisting}[frame=single, language=Javascript]
var ALGOS = ["Soundex", "Metaphone", ...];
var ALGO_SIZES = [763777, 412916, ...];

function updateForm(ss, form) {

  // Obtains a list of the items present on the form
  formItems = form.getItems();

  // Updates the new values
  var algo_index = 0;
  var scale_index = 0;
  for (var i = 0; i < formItems.length; i++)
  {
    if (formItems[i].getType() == "SCALE")
    {
      var rnd_index = Math.floor(Math.random() * 
      ALGO_SIZES[algo_index]) + 1;

      // Obtains the Google Sheets object
      var sheetname = ALGOS[algo_index];
      var sheet = ss.getSheetByName(sheetname);
      var range = sheet.getRange(rnd_index, 1)
      var values = range.getValues();

      // Re-samples from the connected Google Sheets
      _updateScaleTitle(formItems[i], values[0]);

      scale_index++;

      // Moves on to the next metric when a group size is
      // been completed
      if (scale_index != 0)
      {
        if (scale_index % QUESTION_PER_ALGO == 0) {
            algo_index++;
        }
      }
    }
  }
}
\end{lstlisting}
\caption{Section of code from the First Experiment's Google App Script}
\label{fig:GoogleAppScript}
\end{figure}

Figure \ref{fig:GoogleAppScript} contains an interesting snippet from the script used in the experiment. Each time a user submitted their response the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user. This aimed to keep the samplings fair as they are equality likely to appear when attacking the system alongside an ample exploration of the overall match quality.

\section{MainExperiment}
In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.

\todo{What interesting aspects do I want to talk about here?}
